Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-08-21 write-up/fda-recurrent.tex
Updated writing, now allday casestudy

When the window length is too large, i.e., $\Delta > \Delta^\star$, then asymptotically the estimation is unbiased as $\beta(t) \equiv 0$ for $t > \Delta$ and therefore the true function is in the function space; however, in finite samples, we will incur a penalty, especially for settings where the function is far from zero near $t = \Delta$.

we can expect a downward bias in parameter estimates. Moreover, if~$\Delta < \Delta^\star$ then we can expect a similar bias in the parameter estimates.  For the former, however, we can simply let~$K_x = K_b$ grow as a function of data size; for the latter, we can see if~$\hat \beta(s)$ is statistically significant for~$s$ near~$\Delta$. If so, we can set~$\Delta$ larger to ensure the condition holds.

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate} \\ \cline{3-6}
$\Delta=$ & & 0.5 & 1 & 2 & 4 \\ \hline
\multirow{2}{*}{26} & MISE & 0.400 & 0.404 & 0.409 & 0.413 \\
 & Variance & $1.1 \times 10^{-2}$ & $1.3 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $1.9 \times 10^{-2}$ \\ \hline
\multirow{2}{*}{29} & MISE & 0.240 & 0.243 & 0.244 & 0.251 \\
 & Variance & $9.2 \times 10^{-3}$ & $1.1 \times 10^{-2}$ & $1.2 \times 10^{-2}$ & $1.8 \times 10^{-2}$ \\ \hline
\multirow{2}{*}{32} & MISE & 0.105 & 0.103 & 0.103 & 0.105 \\
 & Variance & $8.0 \times 10^{-3}$ & $8.8 \times 10^{-3}$ & $1.0 \times 10^{-2}$ & $1.4 \times 10^{-2}$ \\ \hline
\multirow{2}{*}{35} & MISE & 0.384 & 0.383 & 0.384 & 0.386 \\
 & Variance & $7.0 \times 10^{-3}$ & $7.7 \times 10^{-3}$ & $9.3 \times 10^{-3}$ & $1.1 \times 10^{-2}$ \\ \hline
\multirow{2}{*}{37} & MISE & 0.589 & 0.588 & 0.589, & 0.591 \\
 & Variance & $6.0 \times 10^{-3}$ & $6.5 \times 10^{-3}$ & $7.9 \times 10^{-3}$ & $1.0 \times 10^{-2}$ \\ \hline
\end{tabular}
\caption{Mean-integrated squared error as a function of $\Delta^\star$ and sampling rate when true $\Delta = 30$ minutes.  Demonstrates the }
\label{tab:mise}
\end{table}

@@

1. Start simulation for appendix (delta wrong, beta2)
2. Button Press Figure
3. Compute wear minutes
4. Standardize EDA
5. Subsample EDA and gACC only at wear times between 9am and 8pm
6. EDA/ACC figures
7. Estimate with complete data
8. Estimate with bootMI; make 1 plot with CIs for both compl and bootMI
9. Estimate with heterogeneity
10. Present

>>>>

When the window length is too large, i.e., $\Delta > \Delta^\star$, then asymptotically the estimation is unbiased as $\beta(t) \equiv 0$ for $t > \Delta$; however, we incur a penalty in finite samples, especially for settings where the function is far from zero near $t = \Delta$.  We find the MISE increases and variance slightly decreases as $\Delta$ increases.  While the MISE increased for $\Delta < \Delta^\star$, the pointwise estimation error remains low for $t < \Delta$.  This does not hold for $\Delta > \Delta^\star$, where instead we see parameter attenuation, i.e., a bias towards zero in the estimates at each $0 < t< \Delta$, which is captured by the partial MISE.

\begin{table}[!th]
\begin{tabular}{c | c c c c c}
& & \multicolumn{4}{c}{Sampling rate} \\ \cline{3-6}
$\Delta=$ & & 0.5 & 1 & 2 & 4 \\ \hline
\multirow{3}{*}{26} & MISE & $5.9 \times 10^{-2}$ & $6.1 \times 10^{-2}$ & $6.6 \times 10^{-2}$ & $7.4 \times 10^{-2}$ \\
 & Variance & $1.3 \times 10^{-2}$ & $1.6 \times 10^{-2}$ & $12.4 \times 10^{-2}$ & $3.6 \times 10^{-2}$ \\
  & P-MISE & $7.1 \times 10^{-2}$ & $7.3 \times 10^{-2}$ & $7.8 \times 10^{-2}$ & $8.8 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{29} & MISE & $6.9 \times 10^{-2}$ & $7.0 \times 10^{-2}$ & $7.1 \times 10^{-2}$ & $7.8 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.4 \times 10^{-2}$ \\
  & P-MISE & $7.5 \times 10^{-2}$ & $7.5 \times 10^{-2}$ & $7.7 \times 10^{-2}$ & $8.4 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{32} & MISE & $8.1 \times 10^{-2}$ & $8.0 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.7 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.4 \times 10^{-2}$ & $1.9 \times 10^{-2}$ & $3.3 \times 10^{-2}$ \\
  & P-MISE & $8.1 \times 10^{-2}$ & $8.0 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.7 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{35} & MISE & $9.0 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $8.8 \times 10^{-2}$ & $9.2 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.5 \times 10^{-2}$ & $2.2 \times 10^{-2}$ & $3.0 \times 10^{-2}$ \\
  & P-MISE & $8.5 \times 10^{-2}$ & $8.2 \times 10^{-2}$ & $8.1 \times 10^{-2}$ & $8.4 \times 10^{-2}$ \\ \hline
\multirow{3}{*}{37} & MISE & $10.3 \times 10^{-2}$ & $10.1 \times 10^{-2}$ & $9.9 \times 10^{-2}$ & $10.1 \times 10^{-2}$ \\
 & Variance & $1.1 \times 10^{-2}$ & $1.4 \times 10^{-2}$ & $2.0 \times 10^{-2}$ & $3.0 \times 10^{-2}$ \\
  & P-MISE & $9.4 \times 10^{-2}$ & $9.2 \times 10^{-2}$ & $9.0 \times 10^{-2}$ & $9.0 \times 10^{-2}$ \\ \hline
\end{tabular}
\caption{Mean-integrated squared error (MISE), variance, and partial MISE as a function of $\Delta^\star$ and sampling rate when true $\Delta = 32$ minutes.}
\label{tab:appmise}
\end{table}

@@

1. Start simulation for appendix (delta wrong, beta2): CHECK
2. Button Press Figure:
3. Compute wear minutes:
4. Standardize EDA
5. Subsample EDA and gACC only at wear times between 9am and 8pm
6. EDA/ACC figures
7. Estimate with complete data
8. Estimate with bootMI; make 1 plot with CIs for both compl and bootMI
9. Estimate with heterogeneity
10. Present
